### 2016-03-23 practice/post_thesis/monty_simple_pde_fwd/description.tex
added source-as-influx option; stash to run on workstation

Given these boundary conditions and the alignment of the velocity, axes and boundaries, the weak form of the governing equation with test function $w$ is
\begin{multline*}
\int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
\end{multline*}
where $\Gamma_w$ is the west boundary.

>>>>

Given these boundary conditions and the alignment of the velocity, axes and boundaries, the weak form of the governing equation with test function $w$ is
\begin{multline*}
\int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} w(c\vec{v}\cdot\hat{n}+5) \dA,
\end{multline*}
where $\Gamma_w$ is the west boundary.
